EasyMerge - A New Tool for Code Clones Refactoring

### 2014-03-18 paper/paper.tex
paper updates

three popular Python powered open source projects found on GitHub of different sizes and covers
different usage domains.
They are ``Beets - the media library management system for obsessive-compulsive music geeks", ``Fig - fast, isolated development environments using Docker",
and ``Wagtail - a new Django content management system".

@@

Furthermore,

>>>>

We predict the most famous ones should be better written and contain less code clones in average and we will see if the results stick to our prediction.

@@

Furthermore, the current version of EasyMerge cannot merge similar classes and all duplicated classes are filtered out in preprocessing.
In the future, we can add mechanism to merge similar classes, automatically generate parent classes and extract similar members and methods to the parents.
Additionally, current mergeable clones are within code blocks (at the same indentation level for Python). We are also interested in merging code clones that cross
multiple levels and scopes. We may break big clone fragments into smaller pieces and merge accordingly.
